\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}

% \linespread{0.9}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule ]
\titlespacing*{\section}{0pt}{8pt}{8pt}

\newcommand{\resumeItem}[1]{
  \item{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeSubheadingEducation}[5]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3 - \small#5} & {\small #4} \\
      % \small#5
    \end{tabular*}
}
\newcommand{\resumeSubheadingExperience}[6]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#4} & #3 \\
      {\small#1} - #2 & {\small #5} \\
      \small#6
    \end{tabular*}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}}\\{#2}}

\newcommand{\projectSubItem}[4]
{
    \item{\textbf{#1} - \textit{#4}}\\
    {#2}\\
    {Tech Stack: #3} \\% tech stack
    % {#4}
}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

\noindent
\begin{minipage}[t]{0.35\textwidth}
{\LARGE \textbf{Partho Kunda}}\\
% {\large \textbf{Software Engineer}}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.55\textwidth}
\raggedleft
{\large \href{https://parthokunda.dev}{\textit{\textbf{parthokunda.dev}}}}
\end{minipage}
\hfill

\begin{minipage}[t]{0.35\textwidth}
    % Address: Dhaka, Bangladesh\\
    Email: \href{mailto:parthokunda@gmail.com}{parthokunda@gmail.com}\\
    Mobile: +8801720998327
\end{minipage}
\hfill % Pushes the next minipage to the right
\begin{minipage}[t]{0.55\textwidth} % Middle column for Links
    \raggedleft
    GitHub: \href{https://github.com/parthokunda/}{\textit{github.com/parthokunda}}\\ % Link with small space below
    LinkedIn: \href{https://www.linkedin.com/in/partho-kunda-bb53148b/}{\textit{linkedin.com/in/partho-kunda}}\\
\end{minipage}
\hfill

% \section{Profile}
% Software engineer with nearly 2 years of experience building production systems at Chaldal (YC-backed startup).
% Architected Chaldal's Inventory Platform, optimized API latency and built an ML pipeline.
% Full-stack developer with an interest in system design and infrastructure.
% Proficient in both frontend and backend system, with an interest in distributed systems and infrastructure.
% Currently looking for opportunities to learn and grow myself as an engineer.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingEducation
      {Bangladesh University of Engineering \& Technology}
      {April 2019 -- June 2024}
      {B.Sc. in Computer Science and Engineering}
      {Dhaka, Bangladesh}
      {GPA: 3.90/4.00. Top 22\%}
  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheadingExperience
      {L2 Software Engineer}
      {Supply Chain and Operations Team}
      {July 2024 - Present}
      {Chaldal - \href{https://chaldal.tech/}{\textit{chaldal.tech}} - Y Combinator Startup}{Dhaka, Bangladesh}
      {Tech Stack: C\#, F\#, React, SQL Server, gRPC, Microsoft Orleans, Kubernetes}
      \resumeItemListStart
        \resumeItem{Reduced \href{https://chaldal.com/}{\textit{chaldal.com}} homepage's catalog API latency by 60\% through cache call and DB query optimization.}
        \resumeItem{Implemented the state machine, API and unit testing for Chaldal's Inventory Platform project. The platform serves 250+ active investors and funds approximately 65\% of the inventory demand.}
        \resumeItem{
          Designed a scalable system to track each item's movement across our inventory for Inventory Platform project.
          The system processes $\sim$300K items at a time.}
        \resumeItem {Built a new prediction pipeline and backfilled 6 years of sales data to integrate our core backend with an ML microservice. The model is projected to save at least \$100K per year compared to our previous model.}
        \resumeItem {Took ownership of Inventory Platform and Chaldal Vegetable Network, serving as primary on-call engineer for over a year and resolving 40+ critical production alarms to maintain operational continuity.}
        % \resumeItem {Migrated both backend and frontend of Chaldal Vegetable Network from Service Fabric to Kubernetes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Open Source Contributions}
  \resumeSubHeadingListStart
\projectSubItem{Lazygit}
        {Improved performance in repositories with large number of files by implementing better data structure.}
        {Golang}
        {PR Link: \href{https://github.com/jesseduffield/lazygit/pull/3919}{github.com/jesseduffield/lazygit/pull/3919}}
    \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \projectSubItem
      {Multi Objective Scheduling Framework For Kubernetes}
      {
        Testing framework in Python as part of my undergraduate thesis on the Kubernetes scheduler.
        Helps user test how combining different scheduling algorithms can impact microservices’ performance.
      }
      {Python, Kubernetes, Docker, Prometheus, Grafana, Istio}
      {Repo private as part of ongoing research}

    \projectSubItem
      {Maya Natural Match}
      {Set up CD pipeline, cloud hosting, and analytics for an LLM-based haircare product recommendation site for Maya (Square Group). Serves $\sim$300 daily users.}
      {AWS, Docker, Docker Compose, GitHub Actions}
      {\href{https://maya-naturalmatch.com/}{maya-naturalmatch.com}}

    % \projectSubItem
    %   {Lazygit}
    %   {Improved launch time by $\sim$330x in repositories with a large number of files by implementing efficient data structures.}
    %   {Golang}
    %   {\href{https://github.com/jesseduffield/lazygit/pull/3919}{github.com/jesseduffield/lazygit/pull/3919}}

    % \projectSubItem {Canteen Food Ordering System}
    %   {IoT system showcasing how we can automate food ordering system in our university canteen. Implemented Bluetooth communication using Python.}
    %   {C++, Python, Arduino, Bluetooth}
    %   {\href{https://github.com/parthokunda/Canteen-Food-Ordering-System} {github.com/parthokunda/Canteen-Food-Ordering-System}}

    \projectSubItem{MEDist}
      {Developed a microservice-based platform enabling online patient appointment booking and providing doctors with tools for e-prescribing and managing consultations.}
      {React, Javascript, Tailwind CSS, RabbitMQ}
      {\href{https://github.com/parthokunda/CSE-408-MEDist}
      {github.com/parthokunda/CSE-408-MEDist}}

    % \projectSubItem
    %     {Order Book Generator}
    %     {Developed a command line based application to generate Stock Market's order book by parsing .pcap file.}
    %     {C++}
    %     {\href{https://github.com/parthokunda/MDP-Order-Book-Generator} {github.com/parthokunda/MDP-Order-Book-Generator}}
  \resumeSubHeadingListEnd

\section{Technical Skills}
\textbf{Languages:}{ C\#, F\#, C++, Python, Javascript, Golang, Bash} \\
\textbf{Frameworks \& Libraries:}{ React, Microsoft Orleans, gRPC, RabbitMQ, Tailwind CSS} \\
\textbf{Infrastructure \& DevOps:}{ Kubernetes, Docker, Linux, Git, GitHub Actions, AWS, Prometheus, Grafana, Istio} \\
\textbf{Databases:}{ SQL Server, PostgreSQL, SQLite, MongoDB, Snowflake}


\section{Extracurricular Activities}
  \resumeSubHeadingListStart
    \item
        Achieved Expert rank in Codeforces.
        Link: \href{https://codeforces.com/profile/dont_ask_my_name}{\textit{codeforces.com/profile/dont\_ask\_my\_name}}
    \vspace{-6pt}
    \item
        1st Runner Up in National level Math Olympiad.

    % \item
    %     \textbf{Hobbies:}
    %     Reading books (mostly fantasy novels). Watching club football.
 \resumeSubHeadingListEnd


\end{document}
